### 2015-12-26 extended-abstract.tex
proof first two pages of extended-abstract

In many countries, the crucial actors in the imposition of TTBs are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given TTB is WTO-legal. In the United States, this body is the International Trade Commission (ITC). For ease of exposition and because I would ultimately like to test this theory using U.S. data, I will refer to the actors in this model as lobbies and the ITC. \\

@@

In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product. The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier. Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry. \\

Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO. At this point, the interaction is essentially the same with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff. The essential strategic difference is that at this point the level of the TTB is taken as exogenously set at the level determined in the first round of interaction. \\

@@

Thus we turn to the question of how the ITC decides whether to grant a TTB. The imposition of a TTB, or continuation of one already in place, is not in general costless. We might assume then, that the ITC only grants renewals when it finds the benefits outweigh the costs. If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding. \\

This uncertainty may derive from several sources. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may indirectly reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.

>>>>

In many countries, the crucial actors in the imposition of TTBs are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given TTB is WTO-legal. In the United States, this body is the International Trade Commission (ITC). For ease of exposition and because I would ultimately like to test this theory using U.S. data, I will refer to the actors in this model as industries and the ITC. \\

@@

In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product. The ITC then must decide whether to maintain the MFN tariff or impose the temporary trade barrier. Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry. \\

Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO. At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff. The essential strategic difference is that at this point the level of the TTB is taken as exogenously set at the level determined in the first round of interaction. \\

@@

Thus we turn to the question of how the ITC decides whether to grant a TTB. The imposition of a TTB, or continuation of one already in place, is not in general costless. We might assume then that the ITC only grants renewals when it finds the benefits outweigh the costs. If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding. That is, the industry does not know with precision how the ITC weighs the costs and benefits of granting protection.\\

This uncertainty may derive from several sources. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
